---
title: "Transcranial direct current stimulation of the right frontal eye field in a prosaccade task"
author: Leon Reteig
output:
  html_notebook:
    toc: true
    toc_depth: 2
---

```{r include=FALSE}
# Don't show warnings and messages in HTML output
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

R notebook for statistical analysis of the `sacc-tDCS` dataset. Previous processing:

* Raw data were parsed into events (saccades, fixations, etc.) by the EyeLink data were collected on.
* Events were extracted and saccade measures were computed with a MATLAB script.

# Load data

```{r Load some libraries}
# Load some libraries
library("tidyr") # tidying data frames
library("dplyr") # wrangling data frame data
library("ggplot2") # plotting
library("ez") # ANOVA
library("knitr") # R markdown output (html, pdf, etc.)
library("BayesFactor")
```

The .csv file was created in MATLAB.
```{r Load the data frame, echo=TRUE}
# Load the data frame
dataFile <- file.path("data", "sacc-tDCS_data.csv")
groupData <- read.csv(dataFile, header = TRUE, na.strings = "NaN")

```

```{r Format data frame}
# Format data frame
groupData <- select(groupData, -X) # drop final empty column named "X"
groupData$leg <- factor(groupData$leg, levels = c("pre", "tDCS", "post")) # reorder levels chronologically instead of alphabetically
```

```{r Show data frame}
kable(head(groupData))
```

* __subject__: subject IDj
* __stimulation__: Whether data are from the anodal or cathodal session
* __leg__: Whether data are before (`pre`), during (`tDCS`), or after (`post`) tDCS
* __block__: After each block participant had a brief break and tracker was recalibrated
* __trial__: trial number within a block
* __type__:
    * `lateral` - fixation in center of display, saccade made towards the periphery
    * `center` - fixation in periphery, saccade made back towards the center of the display
* __direction__: `left` for saccades towards the left of current fixation position; `right` for saccades to the right
* __deviation.start__ : distance (in visual angle) from saccade start point to fixation
* __deviation.end__: distance (in visual angle) from saccade end point to target location
* __amplitude__: distance (in visual angle) between saccade start and end point
* __latency__: time (in ms) from target onset to start of saccade

# Basic inspection

##  Reaction time distributions

### Histograms for each subject 

```{r Histogram per subject, fig.width=9.6}
histType <- ggplot(groupData, aes(latency, fill = type)) +
  facet_wrap(~subject, nrow = 3, scales ="free_y") +
  geom_histogram(binwidth = 5, color = "grey50", size = .2) +
  xlim(-50,300)
histType
```

__Stray observations:__

* Center saccades are much faster than lateral, though not to the same degree in all subjects
* Some have a fat short latency tail - too fast saccades that are virtually all towards the center: S05, S10, S11
* Some appear bimodal, but when split for type this is generally because center saccades are faster: S05, S06, S11
* Some are super sharp (S8); others really broad (S01)
* S01 has a very typical looking distribution, but slow

### Stimulation effects across subjects

```{r Density: stimulation across subjects, fig.width=9.6}
dens <- ggplot(groupData, aes(latency, color = stimulation, linetype = leg)) +
  facet_grid(type ~ direction) +
  geom_density() +
  xlim(0, 250) +
  scale_color_brewer(palette = "Set1")
dens
```

### Anodal vs. cathodal in each subject
```{r Density: anodal vs. cathodal per subject, fig.width=9.6}
denstDCS <- ggplot(groupData[groupData$leg == 'tDCS' & groupData$type == "lateral", ], aes(latency, color = stimulation)) +
  facet_wrap(~subject, nrow = 3, scales ="free_y") +
  geom_density() +
  xlim(0, 250) +
  scale_color_brewer(palette = "Set1") +
  ggtitle('Lateral saccades, tDCS block')
denstDCS
```

### Anodal session in each subject

```{r Density: anodal per leg and subject, fig.width=9.6}
densLegAnodal <- ggplot(groupData[groupData$stimulation == 'anodal' & groupData$type == "lateral", ], aes(latency, color = leg)) +
  facet_wrap(~subject, nrow = 3, scales ="free_y") +
  geom_density() +
  xlim(0, 250) +
  ggtitle('Lateral saccades, anodal')
densLegAnodal
```

### Cathodal session in each subject
```{r Density: cathodal per leg and subject, fig.width=9.6}
densLegCathodal <- ggplot(groupData[groupData$stimulation == 'cathodal' & groupData$type == "lateral", ], aes(latency, color = leg)) +
  facet_wrap(~subject, nrow = 3, scales ="free_y") +
  geom_density() +
  xlim(0, 250) +
  ggtitle('Lateral saccades, cathodal')
densLegCathodal
```

# Outliers

## Mark outliers

```{r Outlier criteria, include=FALSE}
tooFast= 50;
tooSlow = 400; 
badFix = 1.8;
badSacc = 8;
```

Criteria for outliers:

* Discard fast saccades, with a latency of `r tooFast` ms or less
* Discard slow saccades, saccades with a latency of `r tooSlow` ms or more
* Discard inaccurate fixations, with saccade starting point more than `r badFix` degrees or more away from fixation
* Discard faulty saccades, with saccade end point more than `r badSacc` degree or more away from the target

In [Kanai et al. (2012)](http://dx.doi.org/10.3389/fpsyt.2012.00045), this was:

* Fast saccades: 50 ms
* Slow saccades: 400 ms
* Bad fixations: 1.8 degrees
* Faulty saccades: opposite hemifield of target (here, that would be 8 degrees as targets were that eccentric)

```{r Mark trials as outliers}
# Mark outliers
groupData <- mutate(groupData, outlier = FALSE, # fill vector with FALSE for all trials
                    outlier = ifelse(latency < tooFast, "fast", outlier), # mark too fast trials as "fast"
                    outlier = ifelse(latency > tooSlow, "slow", outlier), # mark too slow trials as "slow"
                    outlier = ifelse(deviation.start > badFix, "fixation", outlier), # mark bad fixations as "fixation"
                    outlier = ifelse(deviation.end > badSacc, "saccade", outlier)) # mark inaccurate saccades as "saccade"

groupDataClean <- filter(groupData, outlier == FALSE) # make new data frame without outlier trials
```

## Plot outliers per subject

```{r Plot outliers per subject, fig.width=9.6}
outlierPlot <- ggplot(groupData[groupData$outlier != FALSE, ], aes(interaction(stimulation,leg,block,trial), latency, color = outlier, shape = type)) +
  facet_wrap(~subject, nrow = 4, scales = "free_y") +
  geom_point() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = tooFast, linetype = "dashed") +
  geom_hline(yintercept = tooSlow, linetype = "dashed") +
  xlab('Trial') +
  theme(axis.text.x=element_blank(), # remove x-axis (just trial count)
  axis.ticks.x=element_blank())
outlierPlot
```

```{r Table of outlier counts, results='asis'}
outlierCount <- groupData %>%
  group_by(subject) %>%
  summarize(outlier_count = sum(outlier != FALSE, na.rm = TRUE))
kable(outlierCount, caption = "Number of outlier trials per subject")
```

__Stray observations:__

Differences between subjects:

* Some subjects have barely any outliers (S02, S07)
* Most subjects have quite a few outliers, especially S05,S06, S10 and S1. The mean is `r round(mean(outlierCount$outlier_count), digits = 0)` out of `r sum(groupData$subject == "S01")` trials in total
* Only S01 has a sizable amount of slow saccades
* S14 has a lot of negative latencies (and also long positive latencies)
* Those subjects with many fast saccades also tend to have many bad fixations (S06, S10, but see S08)

General patterns:

* Occurence of outliers seems stable throughout the session: there aren't more/less in the beginning / end
* There are very few inaccurate saccades (makes sense, because task is easy and criterion is not strict)
* Most outliers are too fast saccades and bad fixations
* Slow saccades are lateral, fast saccades are to the center, because only the latter are predictable
* Bad fixations appear to be mostly center saccades (but this varies a lot). Perhaps the eyes already drift back towards the center, before executing the saccade?
* Or is the source of bad fixations simply poor quality of the eye tracker data? e.g. people are actually fixating, but due to drift it appears they are not.

# Summary analysis

Here we simply extract median RTs for each condition and use a repeated measures ANOVA for statistical analysis, following [Kanai et al. (2012)](http://dx.doi.org/10.3389/fpsyt.2012.00045).

## Data per block

```{r Compute median in each condition}
# Compute median in each condition
latencyMedian <- groupDataClean %>%
  group_by(subject,stimulation,leg,block,type,direction) %>%
  summarise(latency = median(latency, na.rm = TRUE))
```

### Full factorial plot

```{r Full factorial plot, fig.width=9.6}
# Plot out all the data
fullPlot <- ggplot(latencyMedian, aes(interaction(block,leg), latency, color = stimulation, shape = stimulation)) +
  facet_grid(type ~ direction) +
  stat_summary(fun.y = mean, geom = "point", size = 3) +
  stat_summary(fun.y = mean, geom = "line", aes(group = stimulation), size = 1)
fullPlot
```

There is a pretty sizable difference between the anodal & cathodal sessions in the baseline already: cathodal is always faster than anodal.

The above plot also shows a lot of variability, so it might be best to average over each 3 consecutive blocks so the data come in 15-minute intervals.

## 15-minute intervals (collapse 3 blocks)

```{r Compute median, collapsed across blocks}
# Compute median per leg
latencyMedianLeg <- groupDataClean %>%
  group_by(subject,stimulation,direction,type) %>% 
  summarise(baseline = median(latency[leg == "pre"], na.rm = TRUE), # take average of 3 blocks, make new column
            tDCS = median(latency[leg == "tDCS"], na.rm = TRUE),
            post.1 = median(latency[leg == "post" & block <= 3], na.rm = TRUE),
            post.2 = median(latency[leg == "post" & block >= 4], na.rm = TRUE)) %>%
 gather(leg,latency,baseline,tDCS,post.1,post.2) %>% # gather new columns to use as factor
 mutate(leg = factor(leg, levels = c("baseline", "tDCS", "post.1", "post.2"))) # reorder factor levels
```

### Line plot per leg, individual subjects

Now make the same plot, but for the data collapsed over 3 blocks. Also draw the plot for each individual subject, so we can see which subjects drive the baseline difference, and in which direction the stimulation effect goes for each subject (if there is any).

```{r Line plot for each subject, fig.width=9.6}
kanaiSubsPlot <- ggplot(latencyMedianLeg, aes(leg, latency, color = stimulation, shape = type)) +         
  facet_wrap(~subject, nrow = 5) +
  stat_summary(fun.y = mean, geom = "point", size = 2) +
  stat_summary(fun.y = mean, geom = "line", aes(group = stimulation))
kanaiSubsPlot
```

There are a couple of subjects that show large differences in the baseline already, especially S01.

### Compute magnitude of baseline difference

Let's look at the size of the baseline difference per subject. 

```{r results = 'asis'}
baselineDiff <- latencyMedianLeg %>% 
  filter(leg == "baseline") %>% # keep only baseline data
  spread(stimulation, latency) %>% # make separate columns for anodal and cathodal
  mutate(latency.diff = anodal - cathodal) %>% # subtract the difference
  group_by(subject) %>% 
  summarise(latency.diff = mean(latency.diff))# keep the average difference per subject

kable(baselineDiff, caption = 'Difference between baseline saccade latencies in anodal and cathodal session')
```

There are a few subjects with substantial latency differences between sessions; the three largest of which are all slower in the anodal session (positive values). The mean difference is `r round(mean(baselineDiff$latency.diff), digits = 1)` ms.

### Exclude S01

It seems reasonable to exclude subject 1 from further analysis, because of three things:

* S01 shows the largest baseline difference between the anodal and cathodal sessions.
* Overall, S01 is much slower than all other subjects, by several tens of milliseconds.
* The first session for S01 was aborted because S01 was not feeling well. It was repeated at a later date, so S01 came to the lab 3 times in total instead of two.

However, S01 also seems to show the largest effect of stimulation, for both anodal and cathodal stimulation. It is even in the expected direction: faster saccades than baseline in the anodal session, slower in cathodal.

```{r Exclude S01}
latencyMedianLegExcl <- filter(latencyMedianLeg, subject != "S01") # discard rows from S01
latencyMedianLegExcl$subject <- factor(latencyMedianLegExcl$subject) #remake factor as it now has one level less
```

### Line plot per leg over all subjects

Now that we've excluded subject(s) and collapsed data over blocks, let's look at the group average plot for the first time.

```{r Line plot per leg}
kanaiPlot <- ggplot(latencyMedianLegExcl, aes(leg, latency, color = stimulation, shape = stimulation)) +         
  facet_grid(type ~ direction) +
  stat_summary(fun.y = mean, geom = "point", size = 3) +
  stat_summary(fun.y = mean, geom = "line", aes(group = stimulation), size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.3)
kanaiPlot
```

Even without S01, there is still a small baseline difference of `r round(mean(baselineDiff$latency.diff[baselineDiff$subject != "S01"]), digits = 1)` ms. There also seems to be a tiny effect in the center-left saccade condition that's in the expected direction for both stimulation sessions, but it's about the size of the baseline difference.

## Subtract baseline

The baseline difference is not informative and could obscure real changes from baseline within subjects. Therefore, subtract the baseline from each subsequent measurement.

```{r Subtract baseline}
latencyMedianBaseline <- latencyMedianLegExcl %>%
  group_by(subject,stimulation,direction,type) %>% # for each condition, subtract baseline scores and make new columns
  summarise(tDCS = latency[leg == "tDCS"] - latency[leg == "baseline"], 
           post.1 = latency[leg == "post.1"] - latency[leg == "baseline"],
           post.2 = latency[leg == "post.2"] - latency[leg == "baseline"]) %>%
  gather(leg, latency, tDCS, post.1, post.2)  %>% # gather new columns to use as factor 
  mutate(leg = factor(leg, levels = c("tDCS", "post.1", "post.2"))) # reorder factor levels
```

### Line plots per leg from baseline

```{r Line plot from baseline}
kanaiPlotBase <- ggplot(latencyMedianBaseline, aes(leg, latency, color = stimulation, shape = stimulation)) +         
  facet_grid(type ~ direction) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_summary(fun.y = mean, geom = "point", size = 3) +
  stat_summary(fun.y = mean, geom = "line", aes(group = stimulation), size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.3) +
  coord_cartesian(ylim = c(-15,15))
kanaiPlotBase
```

All changes from baseline are really tiny: 5 ms or less.

### Individual subjects, anodal session

```{r Line plot per subject - anodal}
kanaiPlotBaseSubsAnodal <- ggplot(latencyMedianBaseline[latencyMedianBaseline$stimulation == "anodal", ], aes(leg, latency)) +
  facet_grid(type ~ direction) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(aes(group=subject,color=subject)) +
  stat_summary(fun.y = mean, aes(group = stimulation), geom = "line") +
  stat_summary(fun.y = mean, geom = "point") +
  ggtitle("Anodal difference from baseline")
kanaiPlotBaseSubsAnodal
```

For the center saccades, most subjects follow the expected direction and are below the line. The left-lateral effect that is of primary interest is erratic though: only ~10 subjects are below the line, and none show an online-effect larger than 12 ms.

### Individual subjects, cathodal session

```{r Line plot per subject - cathodal}
kanaiPlotBaseSubsCathodal <- ggplot(latencyMedianBaseline[latencyMedianBaseline$stimulation == "cathodal", ], aes(leg, latency)) +
  facet_grid(type ~ direction) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(aes(group=subject,color=subject)) +
  stat_summary(fun.y = mean, aes(group = stimulation), geom = "line") +
  stat_summary(fun.y = mean, geom = "point") + 
  ggtitle("Cathodal difference from baseline")
kanaiPlotBaseSubsCathodal
```

All of this is split pretty much 50-50, hence the average difference hovering around 0.

# Statistics

## Omnibus anova - saccade latency

__Data__: Outliers removed, collapesed into 15-minute intervals. 

__Dependent measure__: saccadic latency

__Factors__:

* STIMULATION (anodal vs. cathodal)
* LEG (baseline, tDCS, post.1, post.2)
* TYPE (lateral vs. center)
* DIRECTION (left vs. right)

```{r Omnibus ANOVA, results='asis'}
modelOmni <- ezANOVA(data = data.frame(latencyMedianLegExcl), # Repeated over subjects; type 3 sums of squares (cf. SPSS)
                        dv = .(latency), wid = .(subject), within = .(stimulation, leg, type, direction), type = 3)
kable(modelOmni$ANOVA)
```

### Main effect: type

```{r Main effect of type}
latencyMedianLegExcl %>%
  group_by(subject,type) %>%
  summarise(latency = mean(latency)) %>%
  ggplot(aes(type, latency)) +
  stat_summary(fun.data = mean_cl_normal, size = 1) +
  geom_jitter(width = 0.25)
```

This simply reflects that center saccades are faster than lateral saccades, because the location of the target is known.

### Interaction: leg by type

```{r Interaction leg by type}
latencyMedianLegExcl %>%
  group_by(subject,leg,type) %>%
  summarise(latency = mean(latency)) %>%
  ggplot(aes(leg, latency, shape = type)) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line", aes(group = type, linetype = type))
```

The effect of TYPE becomes larger over time: center saccades get faster, lateral saccades become slower.

### Interaction: leg by type by direction

```{r Interaction leg by type by direction}
latencyMedianLegExcl %>%
  group_by(subject,leg,type,direction) %>%
  summarise(latency = mean(latency)) %>%
  ggplot(aes(leg, latency, shape = type)) +
  facet_wrap(~direction) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line", aes(group = type, linetype = type))
```

This interaction of LEG and TYPE appears to occur to a lesser extent for left saccades. The "tDCS" block is the deviant here, but there is no interaction with stimulation.

## ANOVA matching Kanai et al. (2012) - saccade latency

Differing from the previous omnibus analysis, [Kanai et al. (2012)](http://dx.doi.org/10.3389/fpsyt.2012.00045) analysed shifts from baseline and only had lateral saccades.

__Data__: 

* Outliers removed
* Collapsed into 15-minute intervals
* Subtract the baseline from each subsequent block
* Discard center, keep only lateral saccades

__Dependent measure__: saccadic latency

__Factors__:

* STIMULATION (anodal vs. cathodal)
* LEG (tDCS, post.1, post.2)
* DIRECTION (left vs. right)

```{r Kanai ANOVA, results='asis'}

latencyMedianBaselineLateral <- filter(latencyMedianBaseline, type == "lateral") # keep only lateral saccades

modelKanai <- ezANOVA(data = data.frame(latencyMedianBaselineLateral),
                        dv = .(latency), wid = .(subject), within = .(stimulation,leg,direction), type = 3)

# OR, without the EZ package:
# modelKanai=aov(latency~stimulation*leg*direction + Error(subject/(stimulation*leg*direction)),data=latencyMedianBaselineLateral)
# summary(modelKanai)

kable(modelKanai$ANOVA)
```

### Main effect of direction

```{r Main effect of direction}
latencyMedianBaselineLateral %>%
  group_by(subject,direction) %>%
  summarise(latency = mean(latency)) %>%
  ggplot(aes(direction, latency)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_summary(fun.data = mean_cl_normal, size = 1) +
  geom_jitter(width = 0.25)
```

Right saccades become slower with respect to the baseline; left saccades do not. However, the effect is tiny (1-2 ms) and there is no interaction with STIMULATION.

## ANOVA without subtracting baseline, for lateral saccades - saccade latency

Kanai et al. analyzed the baseline-subtracted data; now repeat the same ANOVA with the baseline block still present.

__Data__: 

* Outliers removed
* Collapsed into 15-minute intervals
* Discard center, keep only lateral saccades

__Dependent measure__: saccadic latency

__Factors__:

* STIMULATION (anodal vs. cathodal)
* LEG (tDCS, post.1, post.2)
* DIRECTION (left vs. right)

```{r, Lateral saccade ANOVA, results='asis'}

# keep only lateral saccades
latencyMedianLateral <- latencyMedianLegExcl %>%
  filter(type == "lateral") %>%
  select(-type)

modelLateral <- ezANOVA(data = data.frame(latencyMedianLateral),
                        dv = .(latency), wid = .(subject), within = .(stimulation, leg, direction), type = 3)
kable(modelLateral$ANOVA)

```

### Leg by direction interaction

```{r Interaction leg by direction}
latencyMedianLateral %>%
  group_by(subject,leg,direction) %>%
  summarise(latency = mean(latency)) %>%
  ggplot(aes(leg, latency, shape = direction)) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line", aes(group = direction, linetype = direction))
```

Pretty erratic pattern, and no interaction with STIMULATION either.

## ANOVA without subtracting baseline, for center saccades - saccade latency

Same as previous, but now for center saccades.

```{r, Center saccade ANOVA, results='asis'}
latencyMedianCenter <- latencyMedianLegExcl %>%
  filter(type == "center") %>%
  select(-type)

modelCenter <- ezANOVA(data = data.frame(latencyMedianCenter),
                        dv = .(latency), wid = .(subject), within = .(stimulation, leg, direction), type = 3)
kable(modelCenter$ANOVA)
```

## Bayesian linear mixed effects matching Kanai - saccade latency

### Test against the null model

```{r Compute Bayes Factors cf. null model}
bfKanaiNull = anovaBF(latency~stimulation*leg*direction+subject, data = data.frame(latencyMedianBaselineLateral), whichModels="withmain", whichRandom = "subject", progress = FALSE, iterations = 100000) # compute Bayes Factors
bfKanaiNull = sort(bfKanaiNull, decreasing = TRUE) # sort such that winning model is at the top
```

First we compare all models to the most simple (null) model, which is the intercept only + random effect model: `latency ~ subject`. This does not test for effects of SUBJECT but models it as a nuisance factor (`whichRandom = "subject"`). In addition, to decrease the model space, we do not consider models that have an interaction without the corresponding main effects (`whichModels = "withmain"`).

```{r Extract Bayes Factors withMain, results='asis'}
kable(select(extractBF(bfKanaiNull), bf)) # show only the Bayes factors in a table
```

The winning model is the one with all main effects, with a Bayes factor of `r round(extractBF(bfKanaiNull[1], onlybf = TRUE), digits = 1)`. We can compute the evidence for a particular effect by comparing this winning model with the best-fitting model that does _not_ contain the effect. We can compute the evidence for _absence_ of a particular effect by comparing the winning model with the best-fitting model that _does_ contain the effect.

* STIMULATION. This effect can be quantified by comparing the Bayes factors of the first and the 3rd model : `r round(extractBF(bfKanaiNull[1] / bfKanaiNull[3], onlybf = TRUE), digits = 1)`. This constitues __moderate evidence for the presence of a stimulation effect__.
* DIRECTION. This effect can be quantified by comparing the first and the 2nd model : `r round(extractBF(bfKanaiNull[1] / bfKanaiNull[2], onlybf = TRUE), digits = 1)`. This constitues __anecdotal evidence for the presence of a direction effect__.

* Interaction of STIMULATION and DIRECTION. This term is not in the winning model, and first shows up in the fourth model. The Bayes factor for the comparison of both models is `r round(extractBF(bfKanaiNull[1] / bfKanaiNull[4], onlybf = TRUE), digits = 1)`. This constitues __moderate evidence for the absence of an interaction between stimulation and direction__.
* Interaction of STIMULATION, and LEG. Bayes factor: `r round(extractBF(bfKanaiNull[1] / bfKanaiNull[8], onlybf = TRUE), digits = 1)`. This constitutes __moderate evidence for the absence of an interaction between stimulation and leg__.
* Three-way interaction. Bayes factor: `r round(extractBF(bfKanaiNull[1] / bfKanaiNull[18], onlybf = TRUE), digits = 1)`. This constitutes __strong evidence for the absence of an interaction between stimulation, leg and direction__.

### Test against the full model

Another option for quantifying evidence for a particular effect is to compare the full model to a model where that effect is omitted (`whichModels = top")`. The full model is `stimulation + direction + stimulation:direction + leg + stimulation:leg + direction:leg + stimulation:direction:leg + subject`.

```{r Compute Bayes Factors cf. full model}
bfKanaiFull = anovaBF(latency~stimulation*leg*direction+subject, data = data.frame(latencyMedianBaselineLateral), whichModels="top", whichRandom = "subject", progress = FALSE, iterations = 100000) # compute Bayes Factors
bfKanaiFull
```

Removing the DIRECTION effect from the model yields a lower Bayes Factor, so including this effect improved the model. This thus constitues (some) evidence for the alternative: ` 1 \ ` `r round(extractBF(bfKanaiFull[6], onlybf = TRUE), digits = 3)` ` = ` `r round(extractBF(1/bfKanaiFull[6], onlybf = TRUE), digits = 1)`. The evidence for a stimulation effect is also about the same: `r round(extractBF(1/bfKanaiFull[7], onlybf = TRUE), digits = 1)`.

On the contrary, removing the interactions actually improves the model, so there is moderate evidence for the absence of interaction effects.

All in all, for most effects, the result is qualitatively similar to the approach of testing against the null-model. Only the evidence for absence of the three-way interaction is much, much smaller here.

## Bayesian linear mixed effects with baseline - saccade latency

Repeat the analysis when the baseline is not subtracted, and also for center saccades.

### Lateral saccades

```{r Compute Bayes Factors lateral with-baseline model}

# keep only lateral saccades
latencyMedianLateral <- latencyMedianLegExcl %>%
  filter(type == "lateral") %>%
  select(-type)
  
bfLateral = anovaBF(latency~stimulation*leg*direction+subject, data = data.frame(latencyMedianLateral), whichModels="top", whichRandom = "subject", progress = FALSE, iterations = 100000) # compute Bayes Factors
bfLateral
```

When including the baseline, the evidence for null effects are stronger all around.

### Center saccades

```{r Compute Bayes Factors center with-baseline model}

# keep only center saccades
latencyMedianCenter <- latencyMedianLegExcl %>%
  filter(type == "center") %>%
  select(-type)
  
bfCenter = anovaBF(latency~stimulation*leg*direction+subject, data = data.frame(latencyMedianCenter), whichModels="top", whichRandom = "subject", progress = FALSE, iterations = 100000) # compute Bayes Factors
bfCenter
```

Now the model improves all the time, no matter which effect is omitted.
