---
title: Transcranial direct current stimulation of the right frontal eye field in a
  prosaccade task
author: "Leon Reteig"
subtitle: Frontal Eye Field coordinates
output: 
  html_notebook: 
    highlight: pygments
    toc: true
    toc_float: true
---

R notebook for analysis of frontal eye field coordinates in the `sacc-tDCS` dataset.

# Setup

```{r include=FALSE}
# Don't show warnings and messages in HTML output
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r Load some libraries}
# Load some libraries
library(tidyverse) # importing, transforming, and visualizing data frames
library(knitr) # R markdown output (html, pdf, etc.)
sessionInfo()
```

List the subjects that were excluded in the eye data analyses.

```{r List of subjects to exclude}
subs2exclude <- c("S21","S25","S16","S22","S28")
```

# Coordinates in native space

These were determined for each subject's scan; see `neuronav_notes.md` for further info.

```{r Show native coords, results='asis'}
dataFile <- file.path("data", "FEF_coords_native.csv")
nativeCoords <- read_csv2(dataFile)
nativeCoords %>% 
  select(-folder, -scan) %>% # drop columns with folder and scan names
  filter(!(subject %in% subs2exclude)) %>% # drop rows with excluded subjects
  kable(.)
```

# Transform to MNI space

## Run shell script

`mni_coords.sh` reads in the native coordinates, converts them to MNI space, and writes out a `.csv` of the same format as for the native coordinates.

Under `# FSL setup`, replace `FSLDIR` with the directory path you installed FSL to.

Arguments:

1. __Input:__ csv file with coordinates in native space
2. __Output:__ csv file coordinates in MNI space
3. Passing `all` as a 3rd argument first (re)runs skull stripping and registration to the MNI template.

```{bash}
# FSL Setup
FSLDIR=/usr/local/fsl
PATH=${FSLDIR}/bin:${PATH}
export FSLDIR PATH
. ${FSLDIR}/etc/fslconf/fsl.sh

# Run shell script to compute MNI coordinates
bash src/func/mni_coords.sh data/FEF_coords_native.csv data/FEF_coords_MNI.csv all
```

## MNI coordinates

Load in the MNI coordinates that were written to a `.csv` file by the shell script.

```{r show MNI coords, results='asis'}
dataFile <- file.path("data", "FEF_coords_MNI.csv")
mniCoords <- read_delim(dataFile, ";")
mniCoords <- filter(mniCoords, !(subject %in% subs2exclude)) # exclude subjects
mniCoords %>%
  select(-folder, -scan) %>% # drop columns with folder and scan names
  kable(.)
```

Calculate statistics over subjects:

```{r Descriptives of MNI coordinates, results = 'asis'}
mniCoords %>%
  gather(dimension, coord, MNI_X:MNI_Z) %>%
  group_by(dimension) %>%
  summarise(average = mean(coord), standard.deviation = sd(coord), minimum = min(coord), maximum = max(coord)) %>%
  kable(.)
```

# Create spherical ROI for each coordinate

## Exclude subjects

Write a new `.csv' file with MNI coordinates, without the coordinates from the excluded subjects.

```{r Write new csv without excluded subjects}
exclMNI <- file.path("data", "FEF_coords_MNI_excl.csv")
write_delim(mniCoords, exclMNI, delim = ";")
Sys.setenv(exclMNI = exclMNI) # port variable with csv file name to bash
```

## Run script

The coords can be very nicely visualized with [Surf Ice](https://www.nitrc.org/projects/surfice/) by running the `plot_coords.m` script (requires MATLAB)

Alternatively, `fef_rois.sh` takes the MNI coordinates and adds spherical masks, centered around each subjects FEF coordinate, to the MNI template.

Under `# FSL setup`, replace `FSLDIR` with the directory path you installed FSL to.

Arguments:

1. __Input:__ csv file with coordinates in MNI space
2. __Output:__ NIfTI file of `MNI_152_1mm` template with spherical ROI around each subject's frontal eye field
3. Radius of the spherical ROI in mm

```{bash}

# FSL Setup
FSLDIR=/usr/local/fsl
PATH=${FSLDIR}/bin:${PATH}
export FSLDIR PATH
. ${FSLDIR}/etc/fslconf/fsl.sh

# Run shell script to make spherical ROIs
bash src/func/fef_rois.sh $exclMNI neuronav/FEF_ROIs_bigspheres.nii.gz 2
```